\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{epigraph}
\usepackage{comment}
\usepackage{longtable}
\title {Simplified Virtual Machine\\ INFSEN02-1, INFSEN22-1}
\author{ }
\date { }

\lstset
{
	basicstyle = \ttfamily\small,
	breaklines = true,
	frame = single
}

\begin{document}
\maketitle

The goal of this assignment is to realise a virtual machine, called \textit{Simplified Virtual Machine} (SVM) for a fictional assembly language (\textit{Assembly SVM}). This documents describes the specifications of the SVM and its assembly language. You will be provided with a template for an F\# solution containing a pre-built parser for the assembly language. The parser does the syntax analysis on a program written in SVM Assembly and outputs a data structure representing the program itself, which is described below. Your task is to build the interpreter, which is the component of the virtual machine that executes each statement in the assembly language and alters the state of the memory of the virtual machine. Your implementation must follow the following constraints:

\begin{itemize}
	\item You cannot change in any way the Parser (and thus the language specifications) of Assembly SVM.
	\item You cannot change the semantics (how the statements work) of Assembly SVM.
	\item You cannot use ANY imperative construct/statement other than commands to print on the shell. This means, for instance, no mutable variables, no loops, no mutable data structures, etc.
	\item If you want to use any language other than F\# you must implement a parser for Assembly SVM on your own using the same specifications.
\end{itemize}

\section{Architecture of the SVM}
\input{Sections/architecture}

\section{Interface with the Parser}
\input{Sections/parser}

\section{Syntax of Assembly SVM}
\input{Sections/syntax}

\section{Instruction Behaviours}
\input{Sections/instructions}

\section{Assignment}
\input{Sections/assignment}

\end{document}